### 2012-01-26 GUIErrorDetector/paper/abstract.tex
revise

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms fail to build a sufficiently complete
and precise call graph. Thus, we present a combined RTA and k-CFA
call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms: SWT, Eclipse plugin development framework, Java Swing, and
Android. In an evaluation on XX subjects over XXX LOC, our technique
found a number of real-world errors, suggesting its effectiveness
and showing good scalability.

>>>>

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Heavy use of reflection in modern GUI applications makes existing
call graph construction algorithms fail to build a good
call graph. Thus, we present a method to overcome the limitations, and
build reflection-aware call graphs.

%call graph construction algorithm to overcome the limitations.% of analyzing GUI applications.

We implemented our technique and instantiated it on four popular GUI
platforms: SWT, Eclipse plugin development framework, Java Swing, and
Android. In an evaluation on 9 subjects over 75000 LOC, our technique
found a number of real-world errors, suggesting its effectiveness
and showing good scalability.

### 2012-01-26 GUIErrorDetector/paper/conclusion.tex
revise

We have demonstrated that our technique can be both practical and useful
by an evaluation on XXX subjects acrosss 4 popular GUI
frameworks. Our experiments have shown that we can find bugs
in real-world programs.

@@

\begin{itemize}

\item \textbf{Integration with dynamic and symbolic analyses.} The technique 
presented in this paper is a pure static analysis. It
uses a combined RTA and k-CFA  algorithm to construct a relatively
complete and precise call graph. However, our technique still suffers from
a false positive rate for many GUI applications, due to the conservative
nature of static analysis. A possible way to reduce such false
positives is to integrate the current static analysis with
dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110, ZhangSBE2011}
or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
by employing more accurate information to guide call graph exploration.

\item \textbf{Unit testing multithreaded GUI programs.} Besides
a static analysis,  software testing is another
way to improve software quality.  Although many
GUI testing techniques have been developed recently, few of them can be applied
to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
are interested to investigate how to apply recent advance in automated
software testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
to the context of multithreaded GUI applications.

\item \textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
bugs has become especially critical in the multicore era.
Recently, a few work has been done
on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
the GUI program to fix a revealed bug. Thus, we are interested in 
developing automated error fixing techniques for
multithreaded GUI applications.

\end{itemize}

>>>>

We have demonstrated that our technique can be both practical and useful
by an evaluation on 10 subjects acrosss 4 popular GUI
frameworks. Our experiments have shown that we can find bugs
in real-world programs.

@@

%\begin{itemize}
%\item
\textbf{Integration with dynamic and symbolic analyses.} The technique 
presented in this paper is a pure static analysis. It
uses a combined RTA and k-CFA  algorithm to construct a relatively
complete and precise call graph. However, our technique still suffers from
a false positive rate for many GUI applications, due to the conservative
nature of static analysis. A possible way to reduce such false
positives is to integrate the current static analysis with
dynamic analyses~\cite{Jiang:2008:PPS:1453101.1453110, ZhangSBE2011}
or symbolic analyses~\cite{xie05:symstra, Pasareanu:2011, halfond09issta, BMF97}
by employing more accurate information to guide call graph exploration.

%\item
\textbf{Unit testing multithreaded GUI programs.} Besides
a static analysis,  software testing is another
way to improve software quality.  Although many
GUI testing techniques have been developed recently, few of them can be applied
to unit test multithreaded GUI programs to find potential errors \textit{earlier}. We
are interested to investigate how to apply recent advance in automated
software testing~\cite{Staats:2011:PTO:1985793.1985847, Jagannath:2011:IMU:2025113.2025145, Muccini_Bertolino_Inverardi_2004, Ricca:2001:ATW:381473.381476, Harman:2007}
to the context of multithreaded GUI applications.

%\item
\textbf{Fixing potential GUI errors.} After a potential error is revealed, fixing
it and verifing the patch has often been another important and time-consuming process. Fixing concurrency
bugs has become especially critical in the multicore era.
Recently, a few work has been done
on automatically repairing test script for GUI applications~\cite{Daniel:2011:AGR:2002931.2002937, Huang:2010:RGT:1828417.1828465}. However, none of them focuses on repairing
the GUI program to fix a revealed bug. Thus, we are interested in 
developing automated error fixing techniques for
multithreaded GUI applications.

%\end{itemize}

### 2012-01-26 GUIErrorDetector/paper/related.tex
revise

Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
Harrold:2000:TR:336512.336532}.
 Many GUI analysis and testing techniques have been proposed in the past decade; some have been
implemented as tools and adopted by practitioners. Existing techniques automate
some aspect(s) of GUI testing including model creation
(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
For example,
Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
concurrently running applications. The behavior of the system under test
needs to be specified manually as a labeled transition system. 
Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
is a GUI testing framework for Java and Microsoft Windows applications. 
Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
programs. They proposed a model-based approach for testing GUI-based applications.
Their technique can generate test cases automatically using a structural event
generation graph. 
%Their approach targets Java desktop applications, which
%are quite different from the Android mobile environment (XXXX).
However, testing is often insufficient to ensure the correctness of a GUI program
due to the huge space of possible interactions
with a GUI. The large number of possible interactions
result in a large number of
test inputs requiring substantile human effort.
The second
problem is to determine the coverage of a set of test
cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
using the amount and type of underlying code exercised.
These measures do not work well for GUI testing, because
what matters is not only how much of the code is tested,
but in how many different possible states of the software
each piece of code is tested. This makes it hard to determine
the completeness of a test suite. %All of the (XXXXX, so that GUI is often not well tested)
In contrast, as advocated in this paper, the primary advantage of
using a static analysis is that it can potentially explore
all paths to find possible bugs without actually executing the tested code. % (XXX use heuristic filtering)
Compared with software testing, a static analysis tool may
report false positives due to its conservative nature.
Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
can dramatically reduce the number of false positives  to
an acceptable level.

@@

An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
By exhaustively exploring the thread scheduling space, a model checker can
report counter examples for the potential bugs with a counter example. For example,
CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
a model checker to construct the witness for data races reported by the lockset algorithm.
%(XXXX problem for applying to GUI).
Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
 without compromising the detection capability. To our best knowledge,
we are not aware of any software model checking approach can scale to the subjects
as large as those used in our experiments. Compared with model checking, the static analysis
algorithm presented in this paper chooses call graph as the
abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
access errors instead of being a general property checking tool. For this reason,
our technique achieves good scalability with reasonable precision.

>>>>

Automated GUI testing is a challenging tasks~\cite{Bertolino:2007:STR:1253532.1254712,
Harrold:2000:TR:336512.336532}.
 Many GUI analysis and testing techniques have been proposed in the past decade; some have been
implemented as tools and adopted by practitioners. Existing techniques automate
some aspect(s) of GUI testing including model creation
(for model-based testing)~\cite{androidtesting, Xie:2006:MTC:1172962.1172990},
test-case generation~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007},
test oracle creation~\cite{MemonFSE2000}, test execution~\cite{MemonFSE2001},
and test script repairing~\cite{Huang:2010:RGT:1828417.1828465, Daniel:2011:AGR:2002931.2002937}.
For example,
Kervinen et al.~\cite{Kervinen06model-basedtesting} present a formal model and architecture for testing
concurrently running applications. The behavior of the system under test
needs to be specified manually as a labeled transition system. 
Guitar~\cite{YuanCohenMemonTSE2011, YuanMemonICSE2007, Xie:2006:MTC:1172962.1172990}
is a GUI testing framework for Java and Microsoft Windows applications. 
Yuan and Memon~\cite{YuanMemonICSE2007} generate event-sequence based test cases for GUI
programs. They proposed a model-based approach for testing GUI-based applications.
Their technique can generate test cases automatically using a structural event
generation graph. 
However, testing is often insufficient to ensure the correctness of a GUI program
due to the huge space of possible interactions
with a GUI. The large number of possible interactions
result in a large number of
test inputs requiring substantile human effort.
The second
problem is to determine the coverage of a set of test
cases~\cite{MemonFSE2001}. For conventional software, coverage is measured
using the amount and type of underlying code exercised.
These measures do not work well for GUI testing, because
what matters is not only how much of the code is tested,
but in how many different possible states of the software
each piece of code is tested. This makes it hard to determine
the completeness of a test suite. 
In contrast, as advocated in this paper, the primary advantage of
using a static analysis is that it can potentially explore
all paths to find possible bugs without actually executing the tested code. 
Compared with software testing, a static analysis tool may
report false positives due to its conservative nature.
Nevertheless, as we demonstrated in our experiments, using a few simple heuristics
can dramatically reduce the number of false positives  to
an acceptable level.

@@

An alternative way to find bugs in multithreaded programs is using model checking~\cite{Nori:2010:ESO, Inverardi:2000, Siegel:2008}.
By exhaustively exploring the thread scheduling space, a model checker can
report counter examples for the potential bugs with a counter example. For example,
CHESS~\cite{chess} dynamically explores the thread scheduling decisions to expose
concurrency bugs using a context-bounded approach. Shacham et al~\cite{Shacham:2007} uses
a model checker to construct the witness for data races reported by the lockset algorithm.
Unfortunately, due to the exponential size of the search space,
 it is hard for model checking approaches to scale to a realistic multithreaded GUI application
 without compromising the detection capability. To our best knowledge,
we are not aware of any software model checking approach can scale to the subjects
as large as those used in our experiments. Compared with model checking, the static analysis
algorithm presented in this paper chooses call graph as the
abstraction level with a set of heuristics, and thus is much lightweighted. It is highly tailored to find the invalid thread
access errors instead of being a general property checking tool. For this reason,
our technique achieves good scalability with reasonable precision.
